appendix

### 2023-03-07 paper_comparison/appendix.Rmd
fill in batch analysis

>>>>

```{r batch, fig.cap = "Boxplot of weighted propotion of detect for lineups over different data collection periods."}
vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  mutate(exp = exp - 2) %>%
  group_by(exp, unique_lineup_id) %>%
  mutate(prop_detect = mean(weighted_detect)) %>%
  group_by(exp, unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  ggplot() +
  geom_boxplot(aes(x = factor(exp), y = prop_detect)) +
  facet_grid(~type) +
  scale_x_discrete(labels = c("I", "II", "III")) +
  ylab("Weighted propotion of detect") +
  xlab("Data collection period")
```

```{r}
t_test_poly <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  mutate(exp = exp - 2) %>%
  group_by(exp, unique_lineup_id) %>%
  mutate(prop_detect = mean(weighted_detect)) %>%
  group_by(exp, unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "non-linearity") %>%
  t.test(prop_detect ~ exp, data = .)
```

```{r}
t_test_heter <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  mutate(exp = exp - 2) %>%
  group_by(exp, unique_lineup_id) %>%
  mutate(prop_detect = mean(weighted_detect)) %>%
  group_by(exp, unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type != "non-linearity") %>%
  t.test(prop_detect ~ exp, data = .)
```

We have the same type of model collected over different data collection periods, that may lead to unexpected batch effect. Figure \ref{fig:batch} shows the weighed proportion of detect over different data collection period. The weighted proportion of detect is calculated by taking the average of $c_i$ of a lineup over a data collection period. According to the graph, the distribution for the heteroskedasticity patterns are almost identical in period II and III, while the distribution for the non-linearity patterns have a shift in the median. However, this difference is not statistically significance. The $p$-values of the t-test for testing the mean difference across data periods are `r round(t_test_poly$p.value, 2)` and `r round(t_test_heter$p.value, 2)` for non-linearity and heteroskedasticity patterns respectively. Both are much greater than 5%. Therefore, there is no clear evidence of batch effect.
